Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-11-02 manuscript/text_reuse.tex
added results from diffusion analysis and cleaned up data list

\subsection{Tasks}
\begin{itemize}
\item Write paragraph about how it would be great if text-reuse could be used to classify policy overlap (BD)
\item Write paragraph on why this is not easy (FL)
\end{itemize}

@@

This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the full bill text and the following additional metadata:
\begin{itemize}
    \item action_dates:
        \begin{itemize}
            \item first
            \item last
            \item passed lower
            \item passed upper
            \item signed
        \end{itemize}
    \item actions (a list of legislative actions. E.g. referred to a committee)
        \begin{itemize}
            \item actor
            \item date 
            \item related_entities 
            \item type
        \end{itemize}
    \item bill document first
    \item bill document last
    \item bill id
    \item bill title
    \item date created
    \item date introduced
    \item date signed
    \item date updated
    \item session
    \item short title
    \item state
    \item summary
    \item sunlight_id
    \item unique id
\end{itemize}

@@

\subsection{Tasks}
\begin{itemize}
\item Develop bill metadata dataset (FL)
\begin{itemize}
\item unique bill identifier
\item sponsor identifier from  MALP data
\item state identifier
\item chamber identifier
\item Introduction date
\item Anything else, even if some is missing (status, committees, etc)
\end{itemize}
\item Develop bill-to-bill edgelists (FL)
\begin{itemize}
\item Sparse dyadic dataset (i.e., no observations when there is 0 alignment/overlap)
\item alignment score(s)
\item name of a text file in which aligned text is stored
\end{itemize}
\item Topic models, possibly of a relational form, applied to aligned text
\item Computationally intensive analysis of bill-to-bill alignment and sponsor ideology.
\item Analysis of alignment aggregated at the state level.

>>>>

\subsection{Tasks}
\begin{itemize}
\item
\end{itemize}

@@

This collection of bills is based on all bills that are available through the \url{openstates.org} API. Open states is a website maintained by the Sunlight Foundation, in order to increase transparency in state politics. The Sunlight Foundation use web scrapers to access all bills that are available on the websites of legislatures in all US states. This includes enacted legislation as well as bill that is still in the legislative process, or where not enacted. The database contains the full bill text and the following additional metadata:

\begin{itemize}
    \item action\_dates:
        \begin{itemize}
            \item first
            \item last
            \item passed lower
            \item passed upper
            \item signed
        \end{itemize}
    \item actions (a list of legislative actions. E.g. referred to a committee)
        \begin{itemize}
            \item actor
            \item date 
            \item related\_entities 
            \item type
        \end{itemize}
    \item bill document first
    \item bill document last
    \item bill id
    \item bill title
    \item date created
    \item date introduced
    \item date signed
    \item date updated
    \item session
    \item short title
    \item state
    \item summary
    \item sunlight\_id
    \item unique id
\end{itemize}

@@

\subsection{Diffusion networks and Text re-use}

\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Coefficient & p-value \\ 
  \hline
Intercept & 141.0802 & 0.0000 \\ 
  Diffusion Tie & 5.7258 & 0.0708 \\ 
   \hline
\end{tabular}
\end{table}

\subsection{Tasks}
\begin{itemize}
\item Develop bill metadata dataset (FL)
\begin{itemize}
\item unique bill identifier
\item sponsor identifier from  MALP data
\item state identifier
\item chamber identifier
\item Introduction date
\item Anything else, even if some is missing (status, committees, etc)
\end{itemize}
\item Develop bill-to-bill edgelists (FL)
\begin{itemize}
\item Sparse dyadic dataset (i.e., no observations when there is 0 alignment/overlap)
\item alignment score(s)
\item name of a text file in which aligned text is stored
\end{itemize}
\item Topic models, possibly of a relational form, applied to aligned text
\item Computationally intensive analysis of bill-to-bill alignment and sponsor ideology.
\begin{itemize}
\item Get big sample of bills
\item Assess relationship between alignment between bills and ideological similarity between sponsors
\end{itemize}
\item Analysis of alignment aggregated at the state level.
\begin{itemize}
\item How do we score overlap at the bill and state level?
\end{itemize}
